---
title: "Assignment 1"
subtitle: CRD 150, Lab #
author: YOUR FULL NAME HERE
date: Due by 12:00 am, October 5th on Canvas
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Look up the help documentation for the function `rep()`. How would you use this function to create the following 3 vectors. (Each question is worth 1 point).

a. [1] 0 0 0 0 0

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

b. [1] 1 2 3 1 2 3 1 2 3 1 2 3

```{r warning=FALSE, message = FALSE}
#Insert your code here
```


c. [1] 4 5 5 6 6 6

```{r warning=FALSE, message = FALSE}
#Insert your code here
```


2. What are the differences and similarities between the output produced by a data frame and the equivalent tibble for the following operations. (Each question is worth 1 point).
a. nyctib\$year, nycdf\$year
b. nyctib[,1], nycdf[,1]


3. How much programming experience do you have? Select one: (a) Never programmed before, (b) Some experience, (c)Extensive experience. (1 point)


4. How would you rate your familiarity with the R programming language? Select one: (a) Never used, (b) Installed on machine but don't really use, (c) Basic competence, (d) R Wizard. (1 point)



5. Which of the following statistics concepts have you covered in previous classes? Select all that apply: means and medians, standard deviations, statistical hypothesis testing, t-tests, analysis of variance, linear regression, pvalues, geographic information systems, spatial autocorrelation. (1 point)



6. What are you hoping to get out of this class? (1 point)



7. In this class we will be studying cities.  Identify one U.S. city you would like to learn more about and briefly explain why. (1 point)



