---
title: "Assignment 5"
subtitle: CRD 150
author: YOUR FULL NAME HERE
date: Due by 12:00 am, November 2nd on Canvas
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message = FALSE}
#Insert the code from lab that creates the objects sac.tracts.sp, sacb, sacw, and sacb.lag
```

1. Explain the results of the following commands (1 point each)
a. sacb[[1]]
b. plot(sac.tracts.sp)
   plot(sacb, coordinates(sac.tracts.sp), add=TRUE, col="red")
c. sacw$weights[[1]]
d. sacb.lag[1]

2. You will be using the shapefile sacmetrotracts_race.shp, which you can download from the Assignments Lab 5 folder on Canvas. The file contains census tract data on race/ethnicity composition in the Sacramento Metropolitan Area. The file is clean and ready for analysis. A record layout of the data can be found [here](https://raw.githubusercontent.com/crd150/data/master/assgn5_question2_codebook.txt). Bring the file into R. Use Queen contiguity and row standardized weights unless instructed otherwise.

a. Visually examine the presence of spatial autocorrelation for percent non-Hispanic white, percent non-Hispanic black, percent non-Hispanic Asian, and percent Hispanic. Briefly explain whether you think spatial autocorrelation exists for each of these variables. (3 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

b. Calculate Moran's I for each percent race/ethnicity variable. Which race/ethnicity exhibits spatial autocorrelation? (3 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

c. In words, explain and interpret what each of the following results are showing after running the function `moran.mc()` on the variable percent Hispanic: data, weights, number of simulations, statistic, observed rank and p-value. (3 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```


3. An important use of hot spot analysis is to identify ethnic enclaves. Use the Local Getis-Ord $G_i^*$ statistic to map black, Hispanic, and Asian hot spots (or enclaves) and cold spots in the Sacramento Metropolitan Area using Queen contiguity and row standardized weights. (3 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

4. Designate ethnic enclaves as tracts with Z-scores greater than 1.96 (or 5% significance level).  Describe these ethnic enclaves:

a. You already have percent poverty preloaded into the file. What is the mean poverty rate of black, Hispanic, and Asian enclaves? (1 point)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

b. Bring in three other characteristics into your dataset using the Census or PolicyMap. Calculate their means for black, Hispanic, and Asian enclaves.  Present these characteristics along with mean poverty by ethnic enclave in a presentation-ready table (using the principles outlined in Week 2). Describe what the table is showing, specifically highlighting differences between the three enclaves.  Submit this table in a word document. (4 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```
