---
title: "Assignment 4"
subtitle: CRD 150
author: YOUR FULL NAME HERE
date: Due by 12:00 am, October 26th on Canvas
output: 
  html_document:
    theme: cosmo
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message = FALSE}
#Insert the code from lab that creates the objects sf.metro.tracts.w, ca.tracts and sac.city.tracts.c
```

1. Describe which "pitfalls" - Spatial Autocorrelation, the Modifiable Areal Unit Problem, the Ecological Fallacy, Scale, Nonuniformity of Space, and Edge Effects - each of the following scenarios fall under. Briefly explain your answer. (1 point each)

a. The correlation between percent non-Hispanic black and percent poverty is 0.8 at the Census block level, 0.4 at the block group level, 0.2 at the tract level, and -0.2 at the county level.

b. The scatterplots below show the same data - each point represents an indivdual plotted based on their values for *x* and *y*.  The right scatterplot color codes each individual based on their county of residence, with correlations calculated for each county.

c. A researcher concludes that full-service banks in Los Angeles are spatially inaccessible to Hispanic neighborhoods. The researcher bases his conclusion on the location of banks within Los Angeles City boundaries.  The map below shows Los Angeles City census tracts by percent Hispanic and the location of full-service banks  

d. The two figures below show the same area. The values represent the mean of a variable.  

2. The left-hand side picture in the figure below shows census tract GEOID 06067005204 in Sacramento before a clip to the Sacramento city boundary.  The right-hand side picture shows that tract 06067005204 was cut a little over one-half as a result of the clip (the red portion of the tract is kept as a part of Sacramento city). 

Run the following code.  

```{r eval=FALSE}
filter(ca.tracts, GEOID == "06067005204")
filter(sac.city.tracts.c, GEOID == "06067005204")
```

The first line of code provides information on the entire census tract 06067005204 taken from the complete *ca.tracts* file whereas the second shows it for the clipped version of 06067005204 from the *sac.city.tracts.c* file.  What is the median income in both tracts?  Based on this answer, what are you assumming when you clip a tract? (2 points)

3. One can easily lie (or distort the story) with maps.  One of the commonly used tricks for misrepresenting the spatial distribution of phenomena relates to the inapporpriate classificayions of numeric variables.  In the lab guide, we showed quantile breaks of median income in San Francisco.  Using the object *sf.metro.tracts.w*, produce maps using three other classifications.  Does your general impression of where high and low income neighborhoods are located in the city change across the different classifications? (3 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```
  
4. This [article](http://www.latimes.com/nation/la-na-houston-diversity-2017-htmlstory.html) claims that Houston is the most diverse city in the United States.  Create a Houston City (Texas) **sf** object containing the following census-tract level variables: percent poverty, percent non-Hispanic white, percent non-Hispanic black, percent non-Hispanic Asian, and percent Hispanic.  From this data set, accomplish the following tasks.

a. What is the average percent non-Hispanic white, percent non-Hispanic black, percent non-Hispanic Asian, and percent Hispanic in Houston neighborhoods? Would you agree with the article that Houston is a diverse city? (1 point)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

b. Show percent non-Hispanic black, non-Hispanic white, non-Hispanic Asian, and Hispanic on a 2 x 2 facet map using quantile breaks. Hint: You will need to restructure your data set. (2 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```

c. From (b), is your general impression that white residents are clustered? What about the other three race/ethnic groups?  (1 point)

d. Create a presentation-ready map showing neighborhoods categorized as poor (poverty rate > 0.20) and not poor.  Based on your maps, briefly describe the spatial association between neighborhood poverty and race/ethnicity in Houston. (2 points)

```{r warning=FALSE, message = FALSE}
#Insert your code here
```
